---
title: "Data Transformation"
sidebar: false
engine: knitr
filters:
  - webr
webr:
  cell-options:
    editor-font-scale: 0.85
    fig-width: 6
    fig-height: 3.7
    out-width: "70%"
---

::: {.callout-note}
## Attribution Note

These exercises have been shamelessly copied from the R-Primers project created by [Andrew
Heiss](https://www.andrewheiss.com/). The original version of Heiss' website is available
[here](https://r-primers.andrewheiss.com/index.html).

You can read Heiss' explanation of how he ported the old *Posit Primers* into the *R-Primers* project in the
[About](/about.html) section.
:::

```{r include = FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6 * 0.618,
  fig.retina = 3,
  dev = "ragg_png",
  fig.align = "center",
  out.width = "70%"
)

source(here::here("R", "helpers.R"))
```

In the second part of this week's practical exercises we will explore techniques transforming data in R.

##

```{r}
#| echo: false
#| results: asis

begin_buttons("transform-data/01-tibbles/index.html")
```
